---
output: pdf_document
---
## Automatic or manual transmission better for mpg(miles per gallon)?
### Interested question
Is automatic or manual transmission better for mpg? 

### Data description
Our used dataset is **mtcars** along with R software.  
**am** is one column in **mtcars**, and it only has two values:

* 0 : automatic transmission
* 1 : manual transmission

```{r setup, echo = FALSE}
library(ggplot2)
```

### Exploratory data analysis
First, let's get some intuitive information from a boxplot between mpg and am. Figure 1 is the plot(in Appendix). And we can have an intuition that **manual transmission is better for miles per gallon**. Next, we will search the right model for mpg.

### Linear regression
We want to establish a linear model for mpg. First, let's try everything in.

```{r}
fit1 <- lm(mpg ~ ., data = mtcars)
summary(fit1)$coef
```

p-values are all greater than 0.05 and the model may contain too many variables that have no relation with mpg. We filter out these variables one by one to get a reasonable model. Finally, the appropriate model is:

```{r}
fit2 <- lm(mpg ~ wt + qsec + am - 1, data = mtcars)
summary(fit2)
```

In our model, all three coefficients are significantly not equal to 0. And the model fits well, as the adjusted R squared is close to 1. We have quantified the mpg difference between automatic and manual transmission. The intepretation is: **holding all other variables constant, there is a 4.2995 rise in mpg from automatic to manual transmission, with a standard error of 1.0241.**

Next, let's do a residual plot. As figure 2 shows, the residuals are just like noise. Figure 3 is the QQ-plot of residuals. And we can see that residuals are almost normal. We are ensured that the model fits well.

### Summary
Manual transmission is better for mpg than automatic transmission. For people who want to save fuel using, manual transmission cars are preferred. And for car manufacturers, it's a good choice to optimize automatic transmission cars fuel use, to optimize the inner engine.


---
## Appendix
```{r figure 1, echo = FALSE, fig.width=7, fig.height=4}
g <- ggplot(data = mtcars, aes(x = factor(am, labels = c("Auto", "Manual")), y = mpg))
g <- g + geom_boxplot() + labs(x = "Transmission")
g <- g + labs(title = "Figure 1: am VS mpg boxplot")
g
```

```{r figure 2, echo = FALSE, fig.width=7, fig.height=4}
qplot(x = 1:length(resid(fit2)), resid(fit2),
      main = "Figure 2: residual plot")
```

```{r figure 3, echo = FALSE, fig.width=4, fig.height=4}
qqnorm(resid(fit2), main = "Figure 3: Normal QQ-plot of residuals")
qqline(resid(fit2), col = "blue")
```

